Modelling the emergence of whisker barrels

### 2019-12-17 paper/briefpaper/brief.tex
Tweaks to final para

It is important to emphasize that the formulation of the model is entirely local, insofar as simulation requires no information to be communicated between thalamic projections, or from a given cortical location to any but those immediately adjacent. Hence the simulations demonstrate how a self-organising system, constrained by genetically specified guidance cues, can faithfully reproduce an arrangement of cell aggregates in one neural structure as a topographic map in another.

The model also shows that the shape of the barrels may be primarily determined by the competitive and cooperative interactions between cells relative to the shape of the cortical field boundary. And that somatotopic map formation does not require the pre-specification of centre-points by as yet undetermined additional developmental mechanisms.

>>>>

It is important to emphasize that the formulation of the model is entirely local, insofar as simulation requires no information to be communicated between thalamic projections, or from a given cortical location to any but those immediately adjacent. Hence the simulations demonstrate how a self-organising system, constrained by genetically specified guidance cues, can faithfully reproduce an arrangement of cell aggregates in one neural structure as a topographic map in another.
%
The model also shows that the shape of the barrels may be primarily determined
by the competitive and cooperative interactions between cells relative to the
shape of the cortical field boundary and that somatotopic map formation does
not require the pre-specification of centre-points by as yet undetermined
additional developmental mechanisms.
